---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE,
               message = FALSE,
               warning = FALSE)
```

```{r checkpointsetup, eval = FALSE}
# This will scan the Rmd file to identify the packages used within, and 
# get the source of the package and store it locally. In order to knit this doc, I had to install.packages("rmarkdown", repos = "https://cran.revolutionanalytics.com")
library(checkpoint)
checkpoint("2016-09-02", 
           checkpointLocation = paste0(getwd(), "/packages"))
```

```{r dothings}
library(MASS)

plot(crabs)
```

```{r checkopts}
# check wd
getwd()
# check repos
getOption("repos")
# check libsS
.libPaths()
# check pkgs
installed.packages()[, "Package"]
```

What have we learned:

- travis doesn't care about these, it will contact CRAN regardless of what's in these dirs:

env:
  global:
  - R_LIBS_USER=~/vignettes/packages/.checkpoint/2016-09-02/lib/x86_64-w64-mingw32/3.3.1
  - R_LIBS_SITE=~/vignettes/packages/.checkpoint/2016-09-02/lib/x86_64-w64-mingw32/3.3.1
  
- travis can't work with 

cran: https://mran.revolutionanalytics.com/snapshot/2016-09-02

or 

repos:
  cran: https://mran.revolutionanalytics.com/snapshot/2016-09-02
  
or 

env:
  global:
  - CRAN: https://mran.revolutionanalytics.com/snapshot/2016-09-02
  - R_LIBS_USER=~/vignettes/packages/.checkpoint/2016-09-02/lib/x86_64-w64-mingw32/3.3.1
  - R_LIBS_SITE=~/vignettes/packages/.checkpoint/2016-09-02/lib/x86_64-w64-mingw32/3.3.1
  - R_PROFILE=~/.Rprofile


